### 2018-08-08 paper/evaluation.tex
last expe

\subsubsection{Traffic and availability} % (fold)
\label{ssub:traffic_and_availability}

@@

  \caption{\label{fig:completion_vs_size}
  Availability of devices and number of messages waiting for reception.}
\end{figure}

>>>>

\subsubsection{Availability of nodes and messages in transit} % (fold)
\label{ssub:traffic_and_availability}

@@

  \caption{\label{fig:avail}
  Availability of devices and number of messages waiting for reception.}
\end{figure}

To assess the performance of \name, another important metric is the rate of online nodes at a time.
Figure~\ref{fig:avail} shows just that (in gray), along with the number of messages that are in transit at a time (in black). 
It takes its data from the same experiment as figure~\ref{fig:bw_and_pending_files}.
The black dotted line is the average number of online nodes throughout the experiment: 15.8\% (it was computed up to the ~500th second where the nodes are killed).

We see that the number of online devices lies around its mean the whole experiment.
The message curve roughly follows the previous figure~\ref{fig:bw_and_pending_files}'s number of pending file exchanges. 
Some spikes are created when two devices are online and exchange many chunks in a small amount of time. 
The spike is shut down when these messages are received by the downloader, or when it suddenly falls offline.
The curve never goes down below 1000 messages in transit before the end of the experiment: these account for messages in offline devices that took very long to reach their end.

Indeed, it is interesting to look at the transmission times of the messages: their mean time in transit is of 22s in this experiment, which is incredibly long.
Looking at the standard deviation, that is of 48s, we understand that the dispersion of the transit time is very high, and that the mean is skewed by 
extremely slow messages (with a maximum transit time of 9m13s).
In last resort, we compute the median of the messages transfer time: 639ms; it means that half messages spend less that this time in the system.

An obvious direction for future work is to implement at Time To Leave (TTL) or other stale-messages-removal policy.

\\
To conclude this section, we have seen that \name could empower users to privately exchange files over a challenging network where only 15.8\% of the infrastructure was available at a time.
Our proposal, \name, allows to nevertheless complete the file exchange with an average probability of 94.4\%, against 41.7\% success rate using classical onion routes
